---
title: "ChatGPT"
author: "People Analytics"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("remotes", repos = "https://cloud.r-project.org")
#remotes::install_github("jcrodriguez1989/chatgpt")

library(readxl)
library(dplyr)
library(chatgpt)


# Coleta chave da API no disco C
Sys.setenv(
OPENAI_API_KEY = 
  read_excel("C:/Users/xxxx/secrets.xlsx") |> 
  filter(service == "chatgpt") |> 
  select(senha) |> 
  as.character()
)
```



## Referências

### Documentação da biblioteca

<https://github.com/jcrodriguez1989/chatgpt>


### ChatGPT parâmetros pra mexer

<https://platform.openai.com/docs/api-reference/completions/create>


### Features

The {chatgpt} R package provides a set of features to assist in R coding. Current existing addins:

-   Ask ChatGPT: Opens an interactive chat session with ChatGPT
-   Comment selected code: Comment the selected code
-   Create variable name: Create a name for a variable that would be assigned the result of this code
-   Document code (in roxygen2 format): Document a function definition, in roxygen2 format
-   Explain selected code: Explain the selected code
-   Find issues in the selected code: Find issues in the selected code
-   Optimize selected code: Optimize the selected code
-   Refactor selected code: Refactor the selected code

*Note: When no code is selected, it will use the whole file's code.*



## Exemplos de código

```{r comentar_codigo}
cat(comment_code(
  "for (i in 1:10) {\n  print(i ** 2)\n}"
  ))
```

```{r documentar_codigo}
cat(document_code(
  "square_numbers <- function(numbers) numbers ** 2"
  ))
```

```{r explicar_codigo}
cat(explain_code(
  "for (i in 1:10) {\n  print(i ** 2)\n}"
  ))
```

```{r achar_problemas_no_codigo}
cat(find_issues_in_code(
  "i <- 0\nwhile (i < 0) {\n  i <- i - 1\n}"
  ))
```

```{r nomear_funcoes}
cat(create_variable_name(
  "sapply(1:10, function(i) i ** 2)"
  ))
```

```{r otimizar_codigo}
cat(optimize_code(
  "i <- 10\nwhile (i > 0) {\n  i <- i - 1\n  print(i)\n}"
  ))
```

```{r testar_funcoes}
cat(create_unit_tests(
  "squared_numbers <- function(numbers) {\n  numbers ^ 2\n}"
  ))
```

```{r refatorar_codigo}
cat(refactor_code(
  "i <- 10\nwhile (i > 0) {\n  i <- i - 1\n  print(i)\n}"
  ))
```
